\phantomsection
\addcontentsline{toc}{chapter}{\textsc{Appendices}}
\renewcommand*{\arraystretch}{1.5}

\appendix

\chapter{Data Management Plan}
\label{appendix:data_management_plan}

A Research Data Management Plan was compiled and can be accessed at the following address:

\url{https://github.com/SergiuTripon/msc-thesis-na-epsrc/blob/master/documents/research-data-management-plan/pdf/15110029_sergiu_tripon_research_data_management_plan.pdf}

\chapter{EPSRC grant data}
\label{appendix:epsrc_grant_data}

\begin{spacing}{0.9}
\begin{longtable}[r]{r|r|p{11.5cm}}
\caption[Topics clustered within each community and sub-community discovered by the optimal solution identified in the experiment on the \textit{Topic-grant} network constructed using the current (2010 to 2016) data set]{Topics clustered within each sub-community of Community 1 discovered by the optimal solution identified in the experiment on the \textit{Topic-grant} network constructed using the current (2010 to 2016) data set. \textbf{C1} stands for Community 1. Rows representing sub-communities are named using second-level labels (1.1, 1.2 and so on).}\\
\label{table:topic_a_current_clusters_appendix}
{} & {}\\
\hline
\endfirsthead
\caption[]{Continued from previous page.}\\
\hline
\endhead
\textbf{C1}
& \textbf{1.1} & {ageing: chemistry/biochemistry, analytical science, biomedical sciences}\\
& \textbf{1.2} & {biomaterials, med.instrument.device\& equip., biomechanics \& rehabilitation, medical imaging, biomedical neuroscience, novel industrial products, development (biosciences), systems neuroscience, drug formulation \& delivery, tissue engineering, mathematical \& statistic psych}\\
& \textbf{1.3} & {drug formulation \& delivery, tissue engineering, mathematical \& statistic psych, bioelectronic devices, medical science \& disease, bioinformatics, microbiology, cells, population ecology, complex fluids \& soft solids, theoretical biology, genomics}\\
& \textbf{1.4} & {biological \& medicinal chem., protein chemistry, catalysis \& enzymology, protein folding / misfolding, chemical biology, structural biology}\\
\hline
\textbf{C2}
& \textbf{2.1} & {artificial intelligence, information \& knowledge mgmt, behavioural \& experimental eco, intelligent measurement sys., comput./corpus linguistics, international law, computational linguistics, marketing, criminal law \& criminology, psychology, criminology, science \& technology studies, governance, social policy}\\
& \textbf{2.2} & {cognitive psychology, image \& vision computing, cognitive science appl. in ict, mental health, composition, music \& acoustic technology, design processes, musical performance, developmental psychology, new \& emerging comp. paradigms, human communication in ict, robotics \& autonomy, human-computer interactions, vision \& senses - ict appl.}\\
& \textbf{2.3} & {macroeconomics, political geography}\\
& \textbf{2.4} & {animal behaviour, networks \& distributed systems, computer sys. \& architecture, organisational studies, data handling \& storage, parallel computing, digital signal processing, rf \& microwave technology, fundamentals of computing, social psychology, industrial-org/occupational, software engineering, international relations theory, system on chip, knowledge management, vlsi design, modelling \& simul. of it sys.}\\
& \textbf{2.5} & {applied arts htp, mobile computing, computer graphics \& visual., multimedia, design engineering, new media/web-based studies, digital art \& design, product design, digital arts htp, social anthropology, manufact. business strategy, social theory, media \& communication studies, time-based media htp}\\
\hline
\textbf{C3}
& \textbf{3.1} & {acoustics, fluid dynamics, aerodynamics, heat \& mass transfer, assess/remediate contamination, microsystems, bioenergy, multiphase flow, coal technology, pollution, combustion, power sys man, prot \& control, control engineering, power systems plant, development geography, rheology, earth engineering, separation processes, electric motor \& drive systems, underwater engineering, energy - conventional, wind power, energy - marine \& hydropower}\\
& \textbf{3.2} & {biochemical engineering, macro-molecular delivery, bioprocess engineering, manufact. enterprise ops\& mgmt, design of process systems, manufacturing machine \& plant, food processing, particle technology, food structure/composition, protein engineering, intelligent \& expert systems}\\
& \textbf{3.3} & {asymmetric chemistry, gas \& solution phase reactions, carbohydrate chemistry, materials characterisation, catalysis \& applied catalysis, materials processing, chemical structure, materials synthesis \& growth, chemical synthetic methodology, physical organic chemistry, co-ordination chemistry, plant physiology, electrochemical science \& eng., plant responses to environment, electromagnetics, reactor engineering, evolution \& populations, surfaces \& interfaces}\\
& \textbf{3.4} & {carbon capture \& storage, instrumentation eng. \& dev., diamond light source, materials testing \& eng., energy storage, mech. \& fluid power transmiss., eng. dynamics \& tribology, oil \& gas extraction, fuel cell technologies}\\
& \textbf{3.5} & {research approaches, synthetic biology}\\
\hline
\textbf{C4}
& \textbf{4.1} & {mathematical aspects of or, microeconomic theory}\\
& \textbf{4.2} & {algebra \& geometry, mathematical physics, continuum mechanics, non-linear systems mathematics, logic \& combinatorics, numerical analysis, mathematical analysis, statistics \& appl. probability}\\
\hline
\textbf{C5}
& \textbf{5.1} & {complexity science, management \& business studies, economics, social stats., comp. \& methods, education, sociology, environmental planning, sustainable energy networks, human geography (general), urban \& land management}\\
& \textbf{5.2} & {animal organisms, energy - nuclear, climate \& climate change, land - ocean interactions, coastal \& waterway engineering, regional \& extreme weather, earth \& environmental}\\
& \textbf{5.3} & {building ops \& management, pavement engineering, civil engineering materials, structural engineering, construction ops \& management, sustainable energy vectors, energy efficiency, waste management, environment \& health, waste minimisation, environmental economics, water engineering}\\
& \textbf{5.4} & {geohazards, survey \& monitoring, ground engineering, transport ops \& management, soil science}\\
\hline
\textbf{C6}
& \textbf{6.1} & {design \& testing technology, optical devices \& subsystems, displays, optical phenomena, electronic devices \& subsys., optoelect. devices \& circuits, lasers \& optics, power electronics, optical communications}\\
& \textbf{6.2} & {biological membranes, magnetism/magnetic phenomena, biophysics, solar technology, condensed matter physics, tools for the biosciences, high performance computing}\\
& \textbf{6.3} & {computational methods \& tools, plasmas - laser \& fusion, fusion, plasmas - technological}\\
& \textbf{6.4} & {atoms \& ions, quantum fluids \& solids, cold atomic species, quantum optics \& information, light-matter interactions, scattering \& spectroscopy}
\end{longtable}
\end{spacing}

\clearpage

\begin{spacing}{0.9}
\begin{longtable}[r]{r|r|p{11.5cm}}
\caption[Topics clustered within each community and sub-community discovered in the \textit{Topic-grant} network constructed using the historical (2000 to 2010) data set]{Topics clustered within each community and sub-community discovered as a result of applying the Louvain community detection algorithm to the \textit{Topic-grant} network constructed using the historical (2000 to 2010) data set. Six of the row names are abbreviated: \textbf{C1} stands for Community 1, \textbf{C2} for Community 2 and so on. Rows representing sub-communities of a community are named using second-level labels (1.1, 1.2, 2.1, 2.2 and so on).}\\
\label{table:topic_a_historical1_clusters_appendix}
{} & {}\\
\hline
\endfirsthead
\caption[]{Continued from previous page.}\\
\hline
\endhead
\textbf{C1}
& \textbf{1.1} & {analytical science, co-ordination chemistry, asymmetric chemistry, combinatorial chemistry, biological \& medicinal chem., electrochemical science \& eng., carbohydrate chemistry, mantle \& core processes, catalysis \& applied catalysis, physical organic chemistry, chemical synthetic methodology, reactor engineering}\\
& \textbf{1.2} & {astron. \& space sci. technol., light-matter interactions, atoms \& ions, magnetism/magnetic phenomena, catalysis \& enzymology, nuclear structure, chemical structure, optical phenomena, cold atomic species, plasmas - laser \& fusion, condensed matter physics, plasmas - technological, galactic \& interstellar astron, quantum fluids \& solids, gas \& solution phase reactions, quantum optics \& information, high performance computing, scattering \& spectroscopy, lasers \& optics, surfaces \& interfaces}\\
& \textbf{1.3} & {bioelectronic devices, medical science \& disease, electronic devices \& subsys., microsystems, instrumentation eng. \& dev., musculoskeletal system, materials characterisation, optical communications, materials processing, optical devices \& subsystems, materials synthesis \& growth, optoelect. devices \& circuits}\\
& \textbf{1.4} & {biological membranes, chemical biology, bionanoscience, protein chemistry, bionanotechnology, protein folding / misfolding, biophysics, structural biology}\\
& \textbf{1.5} & {biomaterials, genomics, bioprocess engineering, particle technology, cells, rheology, complex fluids \& soft solids, separation processes, development (biosciences), stem cell biology, drug formulation \& delivery, synthetic biology, food processing, tissue engineering, food structure/composition}\\
\hline
\textbf{C2}
& \textbf{2.1} & {aerodynamics, manufact. business strategy, control engineering, manufact. enterprise ops\& mgmt, design \& testing technology, manufacturing machine \& plant, electromagnetics
}\\
& \textbf{2.2} & {algebra \& geometry, mathematical aspects of or, animal \& human physiology, mathematical physics, complexity science, multiphase flow, continuum mechanics, non-linear systems mathematics, design of process systems, numerical analysis, evolution \& populations, population ecology, fluid dynamics, statistics \& appl. probability, logic \& combinatorics, theoretical biology, mathematical analysis, upper atmos process \& geospace}\\
& \textbf{2.3} & {acoustics, materials testing \& eng., assess/remediate contamination, mech. \& fluid power transmiss., building ops \& management, pavement engineering, civil engineering materials, structural engineering, coastal \& waterway engineering, transport ops \& management, construction ops \& management, urban \& land management, design engineering, waste management, eng. dynamics \& tribology, waste minimisation, ground engineering, water engineering}\\
\hline
\textbf{C3}
& \textbf{3.1} & {bioenergy, fuel cell technologies, carbon capture \& storage, fusion, electric motor \& drive systems, power sys man, prot \& control, energy - conventional, solar technology, energy - nuclear, sustainable energy networks, energy efficiency, sustainable energy vectors, energy storage, wind power}\\
& \textbf{3.2} & {microbiology, power electronics}\\
& \textbf{3.3} & {coal technology, mining \& minerals extraction, combustion, safety \& reliability of plant, heat \& mass transfer}\\
& \textbf{3.4} & {energy - marine \& hydropower, power systems plant, oil \& gas extraction, underwater engineering}\\
\hline
\textbf{C4}
& \textbf{4.1} & {crop science, soil science}\\
\hline
\textbf{C5}
& \textbf{5.1} & {artificial intelligence, languages \& linguistics, bioinformatics, modelling \& simul. of it sys., biomechanics \& rehabilitation, new \& emerging comp. paradigms, biomedical neuroscience, parallel computing, cognitive science appl. in ict, rf \& microwave technology, computer sys. \& architecture, robotics \& autonomy, digital signal processing, software engineering, fundamentals of computing, system on chip, image \& vision computing, vision \& senses - ict appl., intelligent measurement sys., vlsi design}\\
& \textbf{5.2} & {applied arts htp, media \& communication studies, cultural history, mental health, design htp, mobile computing, design processes, multimedia, digital art \& design, music \& acoustic technology, digital arts htp, networks \& distributed systems, economic \& social history, new media/web-based studies, economics, policy, arts mgmt \& creat ind, intelligent \& expert systems, product design, language acquisition, publishing, language training/educational, social stats., comp. \& methods, management \& business studies, sociology, med.instrument.device\& equip.}\\
& \textbf{5.3} & {cultural studies \& pop culture, pollution, displays, psychology, information \& knowledge mgmt}\\
& \textbf{5.4} & {accelerator r\&d, escience, agricultural systems, human communication in ict, applied linguistics, human geography, archaeology of literate soc., human-computer interactions, comput./corpus linguistics, interpreting \& translation, computer graphics \& visual., medical imaging, drama \& theatre - other, psycholinguistics, education, science-based archaeology, environmental informatics, sociolinguistics, environmental planning}
\end{longtable}
\end{spacing}

\clearpage

\begin{spacing}{0.9}
\begin{longtable}[r]{r|r|p{11.5cm}}
\caption[Topics clustered within each community and sub-community discovered in the \textit{Topic-grant} network constructed using the historical (1990 to 2000) data set]{Topics clustered within each community and sub-community discovered as a result of applying the Louvain community detection algorithm to the \textit{Topic-grant} network constructed using the historical (1990 to 2000) data set. Six of the row names are abbreviated: \textbf{C1} stands for Community 1, \textbf{C2} for Community 2 and so on. Rows representing sub-communities of a community are named using second-level labels (1.1, 1.2, 2.1, 2.2 and so on).}\\
\label{table:topic_a_historical2_clusters_appendix}
{} & {}\\
\hline
\endfirsthead
\caption[]{Continued from previous page.}\\
\hline
\endhead
\textbf{C1}
& \textbf{1.1} & {acoustics, intelligent measurement sys., aerodynamics}\\
& \textbf{1.2} & {coal technology, energy - conventional, combustion, safety \& reliability of plant}\\
& \textbf{1.3} & {bioprocess engineering, heat \& mass transfer, cells, multiphase flow, complex fluids \& soft solids, particle technology, design of process systems, reactor engineering, fluid dynamics, rheology}\\
& \textbf{1.4} & {building ops \& management, transport ops \& management, computer graphics \& visual., urban \& land management, energy efficiency, wind power, intelligent \& expert systems}\\
& \textbf{1.5} & {bioenergy, waste minimisation, waste management, water engineering}\\
\hline
\textbf{C2}
& \textbf{2.1} & {condensed matter physics, materials synthesis \& growth, magnetism/magnetic phenomena, quantum fluids \& solids, materials characterisation, solar technology, materials processing, sustainable energy networks}\\
& \textbf{2.2} & {displays, optoelect. devices \& circuits, electronic devices \& subsys., power electronics, microsystems, system on chip, optical communications, vlsi design, optical devices \& subsystems}\\
& \textbf{2.3} & {atoms \& ions, optical phenomena, cold atomic species, plasmas - laser \& fusion, lasers \& optics, quantum optics \& information, light-matter interactions, scattering \& spectroscopy}\\
\hline
\textbf{C3}
& \textbf{3.1} & {development (biosciences), modelling \& simul. of it sys., drug formulation \& delivery, theoretical biology}\\
& \textbf{3.2} & {algebra \& geometry, mathematical analysis, fundamentals of computing, mathematical physics}\\
& \textbf{3.3} & {continuum mechanics, numerical analysis, logic \& combinatorics, parallel computing, mathematical aspects of or, population ecology, medical science \& disease, statistics \& appl. probability, non-linear systems mathematics}\\
\hline
\textbf{C4}
& \textbf{4.1} & {control engineering, manufacturing machine \& plant, electric motor \& drive systems, mech. \& fluid power transmiss.}\\
& \textbf{4.2} & {bioelectronic devices, mobile computing, cognitive science appl. in ict, multimedia, digital signal processing, networks \& distributed systems, electromagnetics, rf \& microwave technology, human communication in ict, vision \& senses - ict appl., human-computer interactions}\\
& \textbf{4.3} & {assess/remediate contamination, ground engineering, civil engineering materials, materials testing \& eng., coastal \& waterway engineering, music \& acoustic technology, energy - nuclear, oil \& gas extraction, eng. dynamics \& tribology, pavement engineering}\\
& \textbf{4.4} & {construction ops \& management, manufact. business strategy, design \& testing technology, manufact. enterprise ops\& mgmt, design engineering, nuclear structure, design processes, software engineering, information \& knowledge mgmt}\\
& \textbf{4.5} & {artificial intelligence, tools for the biosciences, image \& vision computing, underwater engineering,robotics \& autonomy}\\
\hline
\textbf{C5}
& \textbf{5.1} & {biological \& medicinal chem., chemical synthetic methodology, catalysis \& enzymology, co-ordination chemistry, chemical biology, gas \& solution phase reactions, chemical structure, physical organic chemistry}\\
& \textbf{5.2} & {asymmetric chemistry, catalysis \& applied catalysis, carbohydrate chemistry, combinatorial chemistry}\\
& \textbf{5.3} & {analytical science, plasmas - technological, instrumentation eng. \& dev., surfaces \& interfaces}\\
& \textbf{5.4} & {biomaterials, power systems plant, med.instrument.device\& equip., tissue engineering, power sys man, prot \& control}\\
& \textbf{5.5} & {electrochemical science \& eng., mining \& minerals extraction, energy storage, separation processes, fuel cell technologies, sustainable energy vectors}
\end{longtable}
\end{spacing}

\clearpage

\begin{spacing}{0.9}
\begin{longtable}[r]{r|r|p{11.5cm}}
\caption[Topics clustered within each community and sub-community discovered in the \textit{Topic-researcher} network constructed using the current (2010 to 2016) data set]{Topics clustered within each community and sub-community discovered as a result of applying the Louvain community detection algorithm to the \textit{Topic-researcher} network constructed using the current (2010 to 2016) data set. Six of the row names are abbreviated: \textbf{C1} stands for Community 1, \textbf{C2} for Community 2 and so on. Rows representing sub-communities of a community are named using second-level labels (1.1, 1.2, 2.1, 2.2 and so on).}\\
\label{table:topic_b_current_clusters_appendix}
{} & {}\\
\hline
\endfirsthead
\caption[]{Continued from previous page.}\\
\hline
\endhead
\textbf{C1}
& \textbf{1.1} & {building ops \& management, manufact. business strategy, civil engineering materials, pavement engineering, construction ops \& management, robotics \& autonomy, design \& testing technology, soil science, earth engineering, structural engineering, environmental economics, survey \& monitoring, geohazards, waste management, ground engineering, wind power}\\
& \textbf{1.2} & {animal organisms, environment \& health, climate \& climate change, food processing, coastal \& waterway engineering, land - ocean interactions, earth \& environmental, water engineering, energy - marine \& hydropower}\\
& \textbf{1.3} & {aerodynamics, intelligent measurement sys., complexity science, management \& business studies, education, social stats., comp. \& methods, energy efficiency, sociology, environmental planning, sustainable energy networks, human geography (general), transport ops \& management, intelligent \& expert systems, urban \& land management}\\
\hline
\textbf{C2}
& \textbf{2.1} & {cognitive psychology, information \& knowledge mgmt, comput./corpus linguistics, marketing, computational linguistics, mental health, design processes, mobile computing, developmental psychology, psychology, human communication in ict, social theory, human-computer interactions}\\
& \textbf{2.2} & {behavioural \& experimental eco, mathematical \& statistic psych, criminal law \& criminology, media \& communication studies, criminology, modelling \& simul. of it sys., governance, organisational studies, international law, social policy, knowledge management, social psychology}\\
& \textbf{2.3} & {bioinformatics, design engineering, biomedical neuroscience, new \& emerging comp. paradigms, cognitive science appl. in ict, research approaches, control engineering, vision \& senses - ict appl.}\\
& \textbf{2.4} & {computer sys. \& architecture, parallel computing, data handling \& storage, political geography, fundamentals of computing, product design, industrial-org/occupational, software engineering, international relations theory, underwater engineering, networks \& distributed systems, vlsi design}\\
& \textbf{2.5} & {animal behaviour, macroeconomics, applied arts htp, multimedia, artificial intelligence, music \& acoustic technology, composition, musical performance, computer graphics \& visual., new media/web-based studies, digital art \& design, science \& technology studies, digital arts htp, social anthropology, digital signal processing, time-based media htp, image \& vision computing}\\
\hline
\textbf{C3}
& \textbf{3.1} & {genomics, theoretical biology}\\
& \textbf{2.2} & {algebra \& geometry, non-linear systems mathematics, continuum mechanics, numerical analysis, logic \& combinatorics, regional \& extreme weather, mathematical analysis, statistics \& appl. probability, mathematical physics}\\
& \textbf{2.3} & {acoustics, microeconomic theory, mathematical aspects of or, rheology}\\
\hline
\textbf{C4}
& \textbf{4.1} & {ageing: chemistry/biochemistry, magnetism/magnetic phenomena, analytical science, materials characterisation, atoms \& ions, materials synthesis \& growth, bioelectronic devices, optical communications, biological membranes, optical devices \& subsystems, biomedical sciences, optical phenomena, bionanoscience, optoelect. devices \& circuits, biophysics, plant physiology, carbohydrate chemistry, plant responses to environment, chemical structure, pollution, cold atomic species, quantum fluids \& solids, complex fluids \& soft solids, quantum optics \& information, condensed matter physics, rf \& microwave technology, displays, scattering \& spectroscopy, electronic devices \& subsys., solar technology, evolution \& populations, surfaces \& interfaces, high performance computing, system on chip, lasers \& optics, tools for the biosciences, light-matter interactions}\\
& \textbf{4.2} & {accelerator r\&d, fuel cell technologies, assess/remediate contamination, fusion, bioenergy, instrumentation eng. \& dev., carbon capture \& storage, manufact. enterprise ops\& mgmt, coal technology, manufacturing machine \& plant, combustion, materials processing, computational methods \& tools, materials testing \& eng., development geography, mech. \& fluid power transmiss., economics, oil \& gas extraction, electric motor \& drive systems, plasmas - laser \& fusion, electromagnetics, plasmas - technological, energy - conventional, power sys man, prot \& control, energy - nuclear, power systems plant, energy storage, sustainable energy vectors, eng. dynamics \& tribology, waste minimisation, food structure/composition}\\
& \textbf{4.3} & {asymmetric chemistry, gas \& solution phase reactions, biochemical engineering, heat \& mass transfer, bioprocess engineering, macro-molecular delivery, catalysis \& applied catalysis, microsystems, chemical biology, multiphase flow, chemical synthetic methodology, particle technology, co-ordination chemistry, physical organic chemistry, design of process systems, protein engineering, diamond light source, reactor engineering, electrochemical science \& eng., separation processes, fluid dynamics, synthetic biology}\\
& \textbf{4.4} & {biological \& medicinal chem., microbiology, biomaterials, novel industrial products, biomechanics \& rehabilitation, population ecology, catalysis \& enzymology, power electronics, cells, protein chemistry, development (biosciences), protein folding / misfolding, drug formulation \& delivery, structural biology, med.instrument.device\& equip., systems neuroscience, medical imaging, tissue engineering, medical science \& disease}\\
\end{longtable}
\end{spacing}